Ornaments as indicators of social changes and cultural practices in northeastern Taiwan before and after European colonial period

### 2019-12-13 analysis/paper/paper.Rmd
update C14 data file and the caption in the code

kableExtra::kable(table_kw_dates,
             caption = "Radiocarbon ages from charcoal samples excavated from Kiwulan (Chen 2007), calibrated using IntCal13 Atmospheric curve. The codes in the context column refer to the excavator's feature labels, cf. ADD CITATION TO THE REPORT HERE")
```

@@

Figure \@ref(fig:plot-counts-by-period) shows the comparison of frequencies of the major classes of ornaments for different the time periods at Kiwulan. The difference in frequencies between the three time periods reflect significant differences in the use of ornaments (chi-square = `r chisq_test_result_stat`, df = `r chisq_test_result_df`, p-value = $`r chisq_test_result_p_value`$). Most ornament types were present before European contact. Ornament frequencies reached a peak during the European period and then dropped during the Chinese period, especially gold-foil beads. This trend can be also seen on other ornaments including carnelian beads, metal rings, and bells. However, glass beads show a different pattern that indicates a higher frequency in the pre-European contact, and then a decrease in the European period and a further decrease in the Chinese period.

>>>>

kableExtra::kable(table_kw_dates,
             caption = "Radiocarbon ages from charcoal samples excavated from Kiwulan (Chen 2007), calibrated using IntCal13 Atmospheric curve. The codes in the context column refer to the excavator's feature labels, cf. Chen 2007")
```

@@

Figure \@ref(fig:plot-counts-by-period) shows the comparison of frequencies of the major classes of ornaments for different time periods at Kiwulan. The difference in frequencies between the three time periods reflect significant differences in the use of ornaments (chi-square = `r chisq_test_result_stat`, df = `r chisq_test_result_df`, p-value = $`r chisq_test_result_p_value`$). Most ornament types were present before European contact. Ornament frequencies reached a peak during the European period and then dropped during the Chinese period, especially gold-foil beads. This trend can be also seen on other ornaments including carnelian beads, metal rings, and bells. However, glass beads show a different pattern that indicates a higher frequency in the pre-European contact, and then a decrease in the European period and a further decrease in the Chinese period.
